---
title: "simpleRegress"
author: "Shauna Breazeal"
date: "April 1, 2021"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Set up regression models

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```
# NECK
## Model LENGTH ~ NECK    

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
new <- data.frame(NECK=bears$NECK [c(5, 15, 23)])
predict(simp,new,se.fit=TRUE)
```


# HEADWTH
## Model LENGTH ~ HEADWTH 

```{r}
simpHW <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simpHW)
summary.lm(simpHW)
```

```{r}
new <- data.frame(HEADWTH=bears$HEADWTH [c(5, 15, 23)])
predict(simpHW,new,se.fit=TRUE)
```


# HEADLEN
## Model LENGTH ~ HEADLEN

```{r}
simpHL <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simpHL)
summary.lm(simpHL)
```

```{r}
new <- data.frame(HEADLEN=bears$HEADLEN [c(5, 15, 23)])
predict(simpHL,new,se.fit=TRUE)
```


# WEIGHT
## Model LENGTH ~ WEIGHT

```{r}
simpWT <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simpWT)
summary.lm(simpWT)
```

```{r}
new <- data.frame(WEIGHT=bears$WEIGHT [c(5, 15, 23)])
predict(simpWT,new,se.fit=TRUE)
```


# CHEST
## Model LENGTH ~ CHEST

```{r}
simpCT <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simpCT)
summary.lm(simpCT)
```

```{r}
new <- data.frame(CHEST=bears$CHEST [c(5, 15, 23)])
predict(simpCT,new,se.fit=TRUE)
```

# CONCLUSIONS


The best model was based on HEADLEN as seen by the adjusted R-squared, the prediction of the length for bears 5, 15, and 23 is   
70.31, 51.94, 58.83. 


The actual lengths of the bears was   
`r bears$LENGTH[c(5, 15, 23)]`.

The error in prediction for bear number 5 is about 8 inches, for bear number 15 the prediction is right on, for bear number 23 the error in prediciton is just under 6 inches.  


